World Heritage Sites on Wikipedia: Cultural Heritage Activism in a Context of Constrained Agency

### 2021-03-31 analysis/paper/paper.Rmd
update rnaturalearth

```{r wh-wiki-content-and-consumption, fig.cap="Content and consumption of Wikipedia articles about CS-WHL. The top row of density plots show the distributions of basic content characteristics of Wikipedia articles about CS-WHL (yellow) compared to 10,000 random Wikipedia articles (grey). The density plots on the lower left show basic characterstics of consumption. The lower right shows a scatterplot of consumption metrics for Wikipedia articles about CS-WHL and labels on the most intensively consumed articles", fig.width=15}
source(here::here("analysis/paper/003-Wikipedia-random-basic-content.R"))
knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_articles_basic.png"))
```

@@

>>>>

```{r wh-wiki-content, fig.cap="Content of Wikipedia articles about CS-WHL. The density plots show the distributions of basic content characteristics of Wikipedia articles about CS-WHL (yellow) compared to 10,000 random Wikipedia articles (grey).", fig.width=15}
source(here::here("analysis/paper/003-Wikipedia-random-basic-content.R"))
knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_articles_basic_content.png"))
```

@@

```{r wh-wiki-consumption, fig.cap="Consumption of Wikipedia articles about CS-WHL. The density plots on the left show basic characterstics of consumption. The right shows a scatterplot of consumption metrics for Wikipedia articles about CS-WHL, with labels on the most intensively consumed articles", fig.width=15}
knitr::include_graphics(here::here("analysis/figures/wh_wikipedia_articles_basic_consumption.png"))
```
